---
knit: "bookdown::render_book"
title: '`r source(here::here("_common.R")); paste(study_name, "Correlates Analyses Report")`'  
author: '`r paste(study_name, "Biostatistics Team")`'
date: "`r format(Sys.time(), '%B %d, %Y')`"
documentclass: book
site: bookdown::bookdown_site
bibliography: [book.bib, packages.bib]
biblio-style: apalike
suppress-bibliography: true
link-citations: yes
colorlinks: yes
graphics: yes
lot: yes
lof: yes
always_allow_html: yes
header-includes:
   - \usepackage{eso-pic,graphicx,transparent,caption,pdflscape,titling} # keep titling last!
   - \usepackage[margin=1in]{geometry}
   - \usepackage{float}
   - \usepackage{subfig}
---




```{r, include = knitr::is_latex_output() & (startsWith(study_name, "Mock") | contain(tolower(data_cleaned), "mock"))}
knitr::asis_output("\\AddToShipoutPictureFG{
  \\AtPageCenter{
    \\makebox[0pt]{\\rotatebox[origin=c]{45}{
      \\scalebox{10}{\\texttransparent{0.3}{MOCK}}}}}}")
```



<!-- ```{r, include = knitr::is_latex_output() & (startsWith(study_name, "ENSEMBLE") & !contain(tolower(data_cleaned), "mock"))} -->
<!-- knitr::asis_output("\\AddToShipoutPictureFG{ -->
<!--   \\AtPageCenter{ -->
<!--     \\makebox[0pt]{\\rotatebox[origin=c]{45}{ -->
<!--       \\scalebox{10}{\\texttransparent{0.3}{Internal Use Only}}}}}}") -->
<!-- ``` -->


# Disclaimers

`r if (!is_ows_trial)'<!--'`

The data presented in the analysis are provided to NIAID in accordance with Clinical Trial Agreement between the parties. The study was funded in part by BARDA under Government Contract No. 75A50120C00034.


\textbf{Statistical Analysis Plan}

The SAP is available at https://doi.org/10.6084/m9.figshare.13198595

`r if (!is_ows_trial)'-->'`


<!-- `r if ( !( grepl("moderna", attr(config::get(config = Sys.getenv("TRIAL")), "config") ) ) )'<!--'` -->


<!-- * The data presented in the analysis originated from the Moderna Sponsored mRNA-1273-P301 clinical study and are provided to NIAID in accordance with Clinical Trial Agreement between the parties. The study was funded in part by BARDA under Government Contract No. 75A50120C00034 -->

<!-- * The preliminary immunogenicity data presented here do not reflect the Sponsors statistical analysis plan and therefore should not be interpreted as a protocol defined read-out of the clinical study. -->

<!-- * These data are not to be disclosed without written permission of Moderna. -->




\textbf{Reproducibility Notice}

This project integrates the virtual environments framework provided by [the
`renv` package](https://rstudio.github.io/renv/) for computational
reproducibility. By taking this approach, all results are generated using a
consistent versioning of both R and several R packages. This version of the
report was built with `r R.version.string`, [pandoc](https://pandoc.org/)
version `r rmarkdown::pandoc_version()`, and the following R packages:

```{r pkg-list, echo=FALSE, results="asis"}
# borrowed from https://github.com/tidymodels/TMwR/blob/master/index.Rmd
deps <- desc::desc_get_deps()
pkgs <- sort(deps$package[deps$type == "Imports"])
pkgs <- sessioninfo::package_info(pkgs, dependencies = FALSE)
df <- tibble::tibble(
  package = pkgs$package,
  version = pkgs$ondiskversion,
  source = gsub("@", "\\\\@", pkgs$source)
)
knitr::kable(df, format = "markdown")
```

To get started with using this project and its `renv` package library, we
first recommend briefly reviewing the [`renv` collaboration
guide](https://rstudio.github.io/renv/articles/collaborating.html).

<!--chapter:end:index_cor.Rmd-->

---
header-includes:
   - \usepackage{float}
output:
  pdf_document: default
  html_document: default
  citation_package: natbib
  number_sections: true
  extra_dependencies: ["caption", "subcaption", "graphicx"]
  toc: true
---

```{r, echo=FALSE, message=FALSE}
message("~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~ running cor_threshold report ~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~")
```


```{r setup, include=FALSE}
#TRIAL <- "janssen_pooled_realADCP"
#Sys.setenv(TRIAL=TRIAL)
#TRIAL <- Sys.getenv("TRIAL")
 

knitr::opts_chunk$set(echo = TRUE)
folder_var <- "cor_threshold"
library(here)
library(dplyr)
print(here::here())
config <- config::get(config = Sys.getenv("TRIAL"))
for(opt in names(config)){
  eval(parse(text = paste0(names(config[opt])," <- config[[opt]]")))
}
 
```

# Univariate CoR: Nonparametric Threshold Modeling (>=s)

An extension of the unadjusted nonparametric threshold-searching approach
developed in @Donovan, the covariate-adjusted TMLE-based approach developed by
van der Laan, Zhang, Gilbert (submitted) is used to estimate the so-called
threshold-response function $E_X[ E[Y \mid S \geq s, X, A = 1] \mid A=1]$ for a
range of thresholds $s$. Here, $X$ is a set of baseline characteristics, $A=1$
represents the vaccine group, $S$ is the biomarker/immune-response/correlate of
interest, and $Y$ is the indicator of infection diagnosis before the reference time point
$t_f$, which is defined as the final observed time of an event. This parameter can be viewed as a causal/covariate-adjusted version of
the parameter $P(Y=1 \mid S \geq s, A=1)$. Intuitively, the threshold-response
at a given threshold is the expected probability of obtaining of acquiring COVID-19 infection diagnosis if
one experiences a marker/immune-response value above that threshold. The variables adjusted for are: baseline behavioral risk score and region. A
number of plots and tables are reported:
\begin{enumerate}
\item A plot and table with risk estimates and point-wise 95\% confidence intervals
\item A plot and table with risk estimates and simultaneous 95\% confidence bands
\item Monotone-corrected versions of 1 and 2.
\end{enumerate}

A reverse cumulative distribution function curve estimated by the IPW NPMLE of
the marker values is superimposed on the threshold-response plots and a dashed
red line is added to mark the threshold value after which no more events are
observed.

The blue dots on the plots represent the risk predictions at marker values where there was an observed case.

 

\newpage

```{r, echo = F, include = F}
 
ci <- "pointwise"
above = TRUE
monotone <- FALSE

```

```{r, echo = F, include = F}
 
ENSEMBLE <- FALSE
if(tolower(TRIAL) %in% c("janssen_pooled_mock", "janssen_pooled_real", "janssen_na_mock", "janssen_na_real", "janssen_la_mock", "janssen_la_real", "janssen_sa_mock", 'janssen_sa_real', "janssen_trial_real")) {
  ENSEMBLE <- TRUE
  
  keys <-  c("D29", "D29IncludeNotMolecConfirmedstart1") 
 
}

if((TRIAL) %in% c("janssen_sa_realPsV", "janssen_pooled_realbAb", "janssen_pooled_realADCP", "janssen_pooled_realPsV",  "janssen_na_realbAb", "janssen_na_realADCP", "janssen_na_realPsV", "janssen_la_realbAb", "janssen_la_realADCP", "janssen_la_realPsV", "janssen_sa_realbAb", "janssen_sa_realADCP"  )) {
  ENSEMBLE <- TRUE
  
  keys <-  c("D29IncludeNotMolecConfirmed", "D29IncludeNotMolecConfirmedstart1") 
 
}

if(tolower(TRIAL) %in% c("hvtn705")) {
  keys <- c("D210") 
}


if(tolower(TRIAL) %in% c("moderna_mock", 
"moderna_real")) {
  keys <- c("D29", "D57") 
}


```


```{r, results="asis", echo = F }
 
 
for(short_key in keys){
  COR <- strsplit(short_key, "_")[[1]][1]
  config.cor <- config::get(config = COR)
  day <- config.cor$tpeak
  tpeak <- config.cor$tpeak
  countAfter1 <- COR == "D29IncludeNotMolecConfirmedstart1"
  
  assays <- config$assays
  time <- paste0("Day", tpeak)
  markers <- paste0("Day", tpeak, assays)


  
  
  
  title <- paste0("Plots and Tables with estimates and ", ci, " confidence intervals"," for day ", day, " markers")
  if(monotone) {
    title <- paste0(title, " (monotone-corrected)")
  }
  if(countAfter1) {
    title <- paste0(title, " (events after 1 day post dose)")
  } else {
    
  }
  cat("##", title, "\n")
   
  for(marker in markers) {
    key <- paste0(short_key, "_", marker)
    
    assay <- gsub(time, "" , marker)
    if(!(assay %in% assays)) {
      assay <- assays[stringr::str_detect(marker, assays)]
    }

    
    res = knitr::knit_child(c(here::here(folder_var, 'sub_report.Rmd')), quiet = TRUE)
    #res = knitr::knit_child(c(here::here( 'sub_report.Rmd')), quiet = TRUE)

    cat(res, sep = '\n')
    cat("\\clearpage", sep = '\n')
  }
  
   
  
  monotone <- TRUE
  
   
  
 title <- paste0("Plots and Tables with estimates and ", ci, " confidence intervals"," for day ", day, " markers")
  if(monotone) {
    title <- paste0(title, " (monotone-corrected)")
  }
  if(countAfter1) {
    title <- paste0(title, " (events after 1 day post dose)")
  } else {
    
  }
  cat("##", title, "\n")
   
  for(marker in markers) {
    key <- paste0(short_key, "_", marker)
    #assay <- assays[stringr::str_detect(marker, assays)]
    assay <- gsub(time, "" , marker)
    
    
    res = knitr::knit_child(c(here::here(folder_var, 'sub_report.Rmd')), quiet = TRUE)
    
    cat(res, sep = '\n')
    cat("\\clearpage", sep = '\n')
  }
}




```



```{r, echo = F , results = "asis" }
ci <- "simultaneous"

for(short_key in keys){
  COR <- strsplit(short_key, "_")[[1]][1]
  config.cor <- config::get(config = COR)
  day <- config.cor$tpeak
  tpeak <- config.cor$tpeak
  countAfter1 <- COR == "D29IncludeNotMolecConfirmedstart1"
  
  assays <- config$assays
  time <- paste0("Day", tpeak)
  markers <- paste0("Day", tpeak, assays)
  
  
  
  title <- paste0("Plots and Tables with estimates and ", ci, " confidence intervals"," for day ", day, " markers")
  if(monotone) {
    title <- paste0(title, " (monotone-corrected)")
  }
  if(countAfter1) {
    title <- paste0(title, " (events after 1 day post dose)")
  } else {
    
  }
  cat("##", title, "\n")
  
  for(marker in markers) {
    key <- paste0(short_key, "_", marker)
    #assay <- assays[stringr::str_detect(marker, assays)]
    assay <- gsub(time, "" , marker)
    res = knitr::knit_child(c(here::here(folder_var, 'sub_report.Rmd')), quiet = TRUE)
    
    cat(res, sep = '\n')
    cat("\\clearpage", sep = '\n')
  }
  
   
  
  monotone <- TRUE
  
   
  
 title <- paste0("Plots and Tables with estimates and ", ci, " confidence intervals"," for day ", day, " markers")
  if(monotone) {
    title <- paste0(title, " (monotone-corrected)")
  }
  if(countAfter1) {
    title <- paste0(title, " (events after 1 day post dose)")
  } else {
    
  }
  cat("##", title, "\n")
   
  for(marker in markers) {
    key <- paste0(short_key, "_", marker)
    #assay <- assays[stringr::str_detect(marker, assays)]
    assay <- gsub(time, "" , marker)

    res = knitr::knit_child(c(here::here(folder_var, 'sub_report.Rmd')), quiet = TRUE)
    
    cat(res, sep = '\n')
    cat("\\clearpage", sep = '\n')
  }
}



```




 

<!--chapter:end:cor_threshold/report.Rmd-->

```{r, echo=FALSE, message=FALSE}
message("~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~ running references ~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~")
```



`r if (knitr::is_html_output()) '
# References {-}
'`

<!--chapter:end:references.Rmd-->

# Appendix

```{r, echo = FALSE, message = FALSE, warning = FALSE}
quiet <- capture.output({
  renv::activate(project = here::here())
  #source(here::here("_common.R"))
})
library(here)
library(digest)

# hash algorithm picked based on https://csrc.nist.gov/projects/hash-functions
hash_algorithm <- "sha256"


# get hash of commit at HEAD
commit_hash <- system("git rev-parse HEAD", intern = TRUE)    
# get hash of input processed data file based on chosen hashing algorithm
processed_file_digest <- digest(file = path_to_data, algo = hash_algorithm)
    


```

* This report was built from the
  [`CoVPN/correlates_reporting`](https://github.com/CoVPN/correlates_reporting)
  repository with commit hash  
  `r system("git rev-parse HEAD", intern = TRUE)`.  
  A diff of the changes introduced by that commit may be viewed at  
  https://github.com/CoVPN/correlates_reporting/commit/`r system("git rev-parse HEAD", intern = TRUE)`


* The `r hash_algorithm` hash sum of the processed file,  
`r paste0(path_to_data)`:  
`r processed_file_digest`

<!--chapter:end:appendix.Rmd-->

